---
title: "Aides Tests"
author: "Avelyn Potot"
date: "November 06, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Scarolina<-read.csv(file="south_carolina_aides.csv",header=TRUE)
korea<-read.csv(file="korea_aides.csv",header=TRUE)
cenAfrica<-read.csv(file="central_africa_aides.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Thailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?Which if any drug would you recommend or tell to avoid for a 32 year old female?  How about a 27 year old male?

#Methods

This study was based on the famous RV_144 Aides Trial in Thailand in 2009. We will use the same technique as we work on this project.We will also use a different test using bartcharts, rowPerc and chisqtestGc on our graphical, numerical, and Inferential resultsn to compare the results of each trial, i.e. the result on drugs to [1] everyone [2]on female [3]male.
We will show and explain each result on every trials(drugs,vaccine,placebo).Basically,we will show 3 results in each variable.

#Results

#Graphical Results

```{r}
contTable<- xtabs(~infected + group, data = Scarolina)
barchart(contTable,
           auto.key = list(
             space = "top",
             title = "male",
             cex.title = 1,
             coulumns = 1),
           stack = FALSE, horizontal = FALSE)
             
```

Base on the chart, it is shown that there are more people of south Carolina who are non-infected are taking drugs and placebo. It looks almost 99% of the total frequency.It look like there is not a lot of people has an Aids.

```{r}
results<- xtabs(~infected + group, data = Scarolina)
barchartGC(results, type = "percent")
```

Base on the barchart, the graph has almost the same result between infected and non-infected of Aids.People who took drug and placebos on non-infected side has the same result. Same goes to the people who are infected and took drugs and placebos has also the same result. There are 50-50 results in the data both from infected and non infected using the same drugs. 

```{r}
scmales<- filter (Scarolina, sex == "M")
resultsM<- results<- xtabs(~infected + group, data = scmales)
barchartGC(resultsM, type = "percent")
```

Base on the graph, It shows that on male data,the non-infected but taking the drug and placebo has the same result. more or less 50% of them.On the side, the infected ones who took placebos has more or less 40% of the result. However, there is a high result of the ones who took drug for Aids. It shows that almost 60% of males who took drugs that has an Aids showing the big chart.Therefore,It is a bad drug because the drug is not working for the males who took it for Aids.


```{r}
scfemales<- filter (Scarolina, sex == "F")
resultsF<- results<- xtabs(~infected + group, data = scfemales)
barchartGC(resultsF, type = "percent")
```

Base on the chart, The females who took drug and placebo on none infected side has the same result.Both showed more or less 50% on each on the data.Female who have aids who took drug has a results of almost 40% of the result. However, those who take placebos for aids got the heighest percent. Therefore,the placebo drug is not helping to the infected female.